---
title: "A Retrospective Analysis of Mussel Monitoring in the Puget Sound"
author:
  - Catherine Wangen:
      email: cwangen@uw.edu
      institute: qerm, safs
      correspondence: true
  - Mark D. Scheuerell:
      email: scheuerl@uw.edu
      institute: wacfwru
      correspondence: true
institute:
  - qerm: Quantitative Ecology and Resource Management, University of Washington, Seattle, WA
  - safs: School of Aquatic and Fishery Sciences, University of Washington, Seattle, WA
  - wacfwru: U.S. Geological Survey Washington Cooperative Fish and Wildlife Research Unit, School of Aquatic and Fishery Sciences, University of Washington, Seattle, WA
output:
  pdf_document:
    highlight: haddock
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
documentclass: article
geometry: margin=1in
linestretch: 1.1
fontsize: 12pt
header-includes:
  - \usepackage{lineno}
  - \linenumbers
bibliography: "references.bib"
csl: "aslo.csl"
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)

## load {knitcitations}
# library("knitcitations")

## clean out any existing .bib files
# cleanbib()

## set pandoc for formatting
options("citation_format" = "pandoc")
```


# Introduction

The purpose of this report is to provide a retrospective analysis of data generated by previous mussel monitoring surveys coordinated under Washington Department of Fish and Wildlife's (WDFW) Toxics Biological Obsevation System (TBiOS). We determine how existing historical mussel contaminant data can be used for in a Toxics in the Nearshore Vital Sign indicator. In addition, we assess the predictive ability of existing sampling rate to predict expected contaminant trends. 

Toxics data was obtained by transplanting relatively uncontaminated mussels from a local aquaculture source to locations along the Puget Sound shoreline, covering a broad range of upland land-use types from rural to highly urban. Mussels were then recovered, and concentrations of several major contaminant classes were measured. Four mussels surveys were performed, with mussels being retrieved in 2013, 2016, 2018, and 2020. Our analysis focuses on polycyclic aromatic hydrocarbons (PAHs), polybrominated diphenyl ethers (PBDEs), and polychlorinated biphenyls(PCBs) due to their significance in both ecosystem and human health.

# Methods

## Data

-explanation of data?
-point to the repo
-somehow say the analysis we did?

## Modeling

We fit a linear mixed model (LMM) to the data of the form,

$$\log(D_{$$


# Results

-maps?
-cloud plots?

-model parameters (this might require a table in an appendix)
-partial R2 for year
-estimated effect of WIRA by year (significance?), also would need a table


# Discussion

-note deficiences in data
-what we can and can't say

# Acknowledgments



\newpage

# References

\setlength{\parindent}{-0.375in}
\setlength{\leftskip}{0.375in}
\setlength{\parskip}{8pt}
\noindent

```{r}
## create ref cited section
# write.bibtex(file = "references.bib")
```


